---
title: "Quiz4_takehome"
author: "Clara Mugnai"
date: "2/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Statement of Integrity: Copy and paste the following statement and then sign your name (by typing it) on the line below.

“All work presented is my own, and I have followed all rules for collaboration.”

-Clara Mugnai


Use the leaflet package and the us.cities data set from the maps package to make a Zoom-able map of the 50 U.S. capital cities. When you click on a marker for a capital city, both the city name and state as well as the pop (population) should be displayed.

Note that, in the us.cities data set, state capitals are given a value of 2 in the capital variable.

A second note is that if you cannot figure out how to get two “things” (in this case name and population) to display in Leaflet, you would just lose a single point for the quiz (so don’t spend too much time on that part unless you are inclined to do so).

```{r}
library(maps)
library(tidyverse)
library(leaflet)

state_df <- ggplot2::map_data("state")

us_citiesdf <- us.cities %>% 
  filter(capital == 2) %>%
  rename(region = country.etc)


capitals_map <- leaflet(state_df)  %>% 
  addTiles() %>% 
  addProviderTiles(providers$Wikimedia) %>% 
  addMarkers(lng = us_citiesdf$long, lat = us_citiesdf$lat, popup = paste("Capital:", us_citiesdf$name, "<br>",
                           "Population:", us_citiesdf$pop))

capitals_map

```

