---
title: "Quiz6_takehome"
author: "Clara Mugnai"
date: "2/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Complete this Quiz in a .Rmd file. Submit a .Rmd and a knitted .html file to GitHub by the due date and time.

“All work presented is my own, and I have followed all rules for collaboration.”

Clara Mugnai


Construct a Shiny app for any data set that we have worked with so far (besides SLU Majors and Tennis) or for any data set you used in STAT/DATA 234. Thirteen points will be given for Shiny apps that:

run,
have at least 2 different inputs,
have at least 1 plot output that looks presentable (e.g. appropriate labels, colour scale, and makes sense to construct).
Then, write a 2 sentence description about the purpose of your app (2 points).

```{r}
library(tidyverse)
pokemon_df <- read_csv("data/pokemon_full.csv")
library(shiny)

# making a shiny site that shows a scatterplot of pokemon weight/height/base experience vs. HP for a specific type. The user picks type and the y for the scatterplot

df_onetype <- pokemon_df %>% filter(Type == "Fire")
ggplot(data = df_onetype, aes_string(x = "height")) + geom_histogram(bins = 12)

ui <- fluidPage(
  sidebarLayout(sidebarPanel(
    selectizeInput("typechoice",
                   label = "Choose a Type of Pokemon", choices = levels(factor(pokemon_df$Type)),
                   selected = "Fire"),
    radioButtons("statchoice", label = "Choose a Statistic",
                 choices = names(pokemon_df)[c(12,13,14)])),
    mainPanel(plotOutput("histplot"))
  )
)

server <- function(input, output, session) {
  
  pokemon_small <- reactive({
    pokemon_df %>% filter(Type == input$typechoice)
  })
   
  output$histplot <- renderPlot({
ggplot(data = pokemon_small(), aes(x = .data[[input$statchoice]])) + geom_histogram(bins = 12, fill = "forestgreen", color = "purple")
  })

}

shinyApp(ui, server)
```

The purpose of this app is to give users a visual of the different distributions of height, weight, and base experience across different types of Pokemon. They get to choose a type and then a stat and see that, for example, electric pokemon are much lighter than rock pokemon. 

